Survival Analysis

### 2014-04-28 paper.Rnw
Start analysis.

\section*{Results}

@@

@@

\section*{Discussion}
% Explain conclusions and interpretations in layman's terms.

>>>>

\section*{Results and Discussion}

@@

Notice that the survival rate drops off sharply after the first feel weeks. For weeks 0 to 5, there is a 25\% drop in survival. In contrast, there is a similar drop in survival for weeks 10 to 20. Casually, we can say that the survival rate for breast feeding improves for the mothers who breast feed longer. Likewise, we can say that the expected duration of breastfeeding is around 10 weeks and that less than 25\% of mothers breast feed for at least the FDA recommended breastfeeding duration.

@@
